TBD

### 2021-02-18 outputs/paper/paper.Rmd
Q9 plot updated to reflect changed parameters

```{r Q9, echo = FALSE, message = FALSE}
### Before the (intervention start date), approximately how much of your total monthly sales revenue came from takeout or delivery?
### Did not offer takeout or delivery
### 15% or less
### 15-30%
### 30-50%
### 50-75%
### 75% or more

ggplot(data = all_simulated_dataset, mapping = aes (x = Q9, fill = type)) +
  geom_bar(position = "stack") +  coord_flip() + 
  scale_x_discrete(limit = c("Did not offer takeout or delivery", "15% or less", "15-30%","30-50%", "50-75%", "75% or more")) + 
  labs(x = "Total Monthly Sales Revenue Fromt Takeout or Delivery",
       y = "# of Restaurants",
       title = "Q9",
       fill = "Legend") +
  theme_minimal()
```

>>>>

```{r Q9, echo = FALSE, message = FALSE}
### Before the (intervention start date), approximately how much of your total monthly sales revenue came from takeout or delivery?
### Did not offer takeout or delivery
### 25% or less
### 25- 50%
### 50-75%
### 75% or more

ggplot(data = all_simulated_dataset, mapping = aes (x = Q9, fill = type)) +
  geom_bar(position = "stack") +  coord_flip() + 
  scale_x_discrete(limit = c("Did not offer takeout or delivery", "25% or less", "25-50%", "50-75%", "75% or more")) + 
  labs(x = "Total Monthly Sales Revenue Fromt Takeout or Delivery",
       y = "# of Restaurants",
       title = "Q9",
       fill = "Legend") +
  theme_minimal()
```
